% List a subset of my volunteer and education history, to help flesh out the view of who I am professionally
\section{Volunteer \mhstandout{Work History}}\label{sec:work-history}
\subsection{\textbf{Director of Technology} at \shstandout{VaginaPagina} \shyears{[2001-2014]}}
VaginaPagina is an online community that offers a supportive, progressive, body- and sex-positive environment in which to discuss issues related to female sexual and reproductive health and wellness.  Beginning as a LiveJournal community, it blossomed\footnote{\href{http://www.dailydot.com/news/vagina-pagina-livejournal-tasha-walston/}{VP in the News}\\ http://bit.ly/1dZo0as} into a volunteer-run nonprofit organization with an anonymous online repository of information.  My responsibilities included developing the web software and managing the domain.  The site used an embedded media wiki to provide a rich online information resource.

\subsection{\textbf{Director of Technology} at \shstandout{Home Alive} \shyears{[2000-2005]}}
Home Alive\footnote{\href{http://web.archive.org/web/20040721083500/http://www.homealive.org/}{HomeAlive Site}\\ http://bit.ly/1hzw99S} was a community-based anti-violence organization that provided affordable self-defense classes, workshops, and educational events for all people within a social change framework.  Over the course of my volunteer time there I managed internal IT, web hosting and email services.  It was an honor to work with all the dedicated volunteers on Capitol Hill in Seattle for such a great cause.

\bigskip
\bigskip

\section{Education \mhstandout{History}}
\subsection{\textbf{Undergrad} at \shstandout{Seattle Pacific University} \shyears[1995-1998]}
At SPU I pursued a double major in Graphic Design and Math for Computer Science.  Eventually as my first business grew I was forced to make a time choice between schooling and running the business.  I chose to focus on growing the company and have not regretted the decision since.
